Rust Bug Fix Patterns

### 2022-09-12 3_results.tex
fix compilation errors

\end{lstlisting} \\

@@

For instance, in the Rust project swc-project/swc (A fast TypeScript/JavaScript compiler), the developer needed to modify the CSS parser source code in a way that it accounts for empty @media queries \footnote{\href{https://github.com/swc-project/swc/commit/75a14f98b7370226115ee24eec6eb8c802bd4837}}, so, as shown in the code snippet above, they changed type MediaQueryList to Option<MediaQueryList>, and modified the other parts of the source code, accordingly.

@@

To give an example, in starship/starship after one of the commits \footnote{\href{https://github.com/starship/starship/commit/56d475578ea508631275772127f49a6949fea6b0}{git_branches.rs}}, the developer borrows the value of $repo\_dir$ to keep the ownership of the object in the current scope. Now this object can then be used in another function invocation ($remove\_dir\_all(repo\_dir)$) which fixes a bug.

@@

\subsubsection{B4. Modification in dereferencing a string prior to calling .to_string()}

@@

\multirow{12}{*}{General}        
& \multirow{2}{*}{Attributes}    & G1  & Adding Attributes to Structs                                        \\
                                 &                                & G2  & Adding Attributes to Struct Fields                                  \\\cline{2-3}
                                 & \multirow{3}{*}{Struct}        & G3  & Adding/Removing a Struct field                                      \\
                                 &                                & G4  & Adding/Removing pub to/from struct field                            \\
                                 &                                & G5  & Different fields order when initializinng Struct                       \\\cline{2-3}
                                 & Option                         & G6  & Changing field type T to Option                                          \\\cline{2-3}
                                 & \multirow{4}{*}{Types}         & G7  & Changing a Struct field type                                        \\
                                 &                                & G8  & Changing a generic type                                             \\
                                 &                                & G9  & Change in enum variant value type                                   \\
                                 &                                & G10 & Changing the type inside a tuple                                         \\\cline{2-3}
                                 & \multirow{2}{*}{Traits}        & G11 & TraitBound Change                                                   \\
                                 &                                & G12 & Implementing a different trait for a struct.                            \\\cline{1-3}
\multirow{13}{*}{Borrow Checker} & \multirow{4}{*}{Ref and Deref} & B1  & Adding \&                                                           \\
                                 &                                & B2  & Removing \&                                                         \\
                                 &                                & B3  & Dropping \& from function declaration and dereferencing match \\
                                 &                                & B4  & Adding *                                                            \\\cline{2-3}
                                 & \multirow{2}{*}{Mut}           & B5  & Adding mut                                                          \\
                                 &                                & B6  & Removing mut                                                        \\\cline{2-3}
                                 & Vector                         & B7  & Vector reference to slice                                           \\\cline{2-3}
                                 & \multirow{3}{*}{Lifetime}      & B8  & Adding generic Lifetime                                             \\
                                 &                                & B9  & Dropping static lifetime                                            \\
                                 &                                & B10 & Dropping Lifetime in field definition                               \\\cline{2-3}
                                 & \multirow{3}{*}{Clone}         & B11 & Dropping clone and adding dereference                               \\
                                 &                                & B12 & Dropping clone                                                      \\
                                 &                                & B13 & Dropping clone and adding reference  & \hline

>>>>

@@

For instance, in the Rust project swc-project/swc (A fast TypeScript/JavaScript compiler), the developer needed to modify the CSS parser source code in a way that it accounts for empty @media queries \footnote{\url{https://github.com/swc-project/swc/commit/75a14f98b7370226115ee24eec6eb8c802bd4837}}, so, as shown in the code snippet above, they changed type MediaQueryList to Option<MediaQueryList>, and modified the other parts of the source code, accordingly.

@@

To give an example, in starship/starship after one of the commits \footnote{\url{https://github.com/starship/starship/commit/56d475578ea508631275772127f49a6949fea6b0}, file \texttt{git\_branches.rs}}, the developer borrows the value of $repo\_dir$ to keep the ownership of the object in the current scope. Now this object can then be used in another function invocation ($remove\_dir\_all(repo\_dir)$) which fixes a bug.

@@

\subsubsection{B4. Modification in dereferencing a string prior to calling .to\_string()}

@@

\multirow{12}{*}{General}        
& \multirow{2}{*}{Attributes}    & G1  & Adding Attributes to Structs                                        \\
                                 &                                & G2  & Adding Attributes to Struct Fields                                  \\\cline{2-3}
                                 & \multirow{3}{*}{Struct}        & G3  & Adding/Removing a Struct field                                      \\
                                 &                                & G4  & Adding/Removing pub to/from struct field                            \\
                                 &                                & G5  & Different fields order when initializinng Struct                       \\\cline{2-3}
                                 & Option                         & G6  & Changing field type T to Option                                          \\\cline{2-3}
                                 & \multirow{4}{*}{Types}         & G7  & Changing a Struct field type                                        \\
                                 &                                & G8  & Changing a generic type                                             \\
                                 &                                & G9  & Change in enum variant value type                                   \\
                                 &                                & G10 & Changing the type inside a tuple                                         \\\cline{2-3}
                                 & \multirow{2}{*}{Traits}        & G11 & TraitBound Change                                                   \\
                                 &                                & G12 & Implementing a different trait for a struct.                            \\\cline{1-3}
\multirow{13}{*}{Borrow Checker} & \multirow{4}{*}{Ref and Deref} & B1  & Adding \&                                                           \\
                                 &                                & B2  & Removing \&                                                         \\
                                 &                                & B3  & Dropping \& from function declaration and dereferencing match \\
                                 &                                & B4  & Adding *                                                            \\\cline{2-3}
                                 & \multirow{2}{*}{Mut}           & B5  & Adding mut                                                          \\
                                 &                                & B6  & Removing mut                                                        \\\cline{2-3}
                                 & Vector                         & B7  & Vector reference to slice                                           \\\cline{2-3}
                                 & \multirow{3}{*}{Lifetime}      & B8  & Adding generic Lifetime                                             \\
                                 &                                & B9  & Dropping static lifetime                                            \\
                                 &                                & B10 & Dropping Lifetime in field definition                               \\\cline{2-3}
                                 & \multirow{3}{*}{Clone}         & B11 & Dropping clone and adding dereference                               \\
                                 &                                & B12 & Dropping clone                                                      \\
                                 &                                & B13 & Dropping clone and adding reference  \&
